Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-21 article_review/reviewer_letter.tex
More changes

To confirm this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling. The comparison is carried out for the bratley \textit{et al.} test function in Section 5.3. Results show that for an equivalent number of evaluations, the random sampling method is less accurate than our procedure.}

@@

\answer{As pointed out by the reviewer, some clarification was needed in this paragraph. We indicated that we extend the use of  Owen's estimator by using Sobol' sequences instead of iid random points.}

@@

{\color{blue} We agree with the reviewer that the effective dimension of the $2d-1$ integrand might be lower than the $d+1$ integrand. However, estimating the effective dimension of each integrand already requires a large number of model evaluations (\textit{c.f.} Wang. X and Fang. K.-T., 2003).

Since evaluating the effective dimension is not in the scope of this paper, we propose the following. The original statement has been replaced with the assumption that the higher dimensions integrand possesses a higher effective dimension. Then, this assumption is tested on each example by comparing the number of evaluations required by each integrand.}
%plotting the repartition of the sum of the $c_j$ (equation (19)) over the $100$ repeats. The sign of the sum tells us if, in average, this assumption is validated across the Sobol' indices.}

>>>>

To confirm this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling. The comparison is carried out for the Bratley \textit{et al.} test function in Section 5.3. Results show that for an equivalent number of evaluations, the random sampling method is less accurate than our procedure.}

@@

\answer{As pointed out by the reviewer, some clarification was needed in this paragraph. We indicated that we extend  Owen's estimator by using Sobol' sequences instead of iid random points.}

@@

{\color{blue} We agree with the reviewer that the effective dimension of the $2d$ integrand in $I_1$ might be lower than the $d+1$ integrand in $I_2$. However, estimating the effective dimension of each integrand already requires a large number of model evaluations (\textit{c.f.} Wang. X and Fang. K.-T., 2003).

Since evaluating the effective dimension is not in the scope of this paper, we propose the following. The original statement has been replaced with the assumption that the integrand in $I_1$ is harder to estimate than the integrand in $I_2$. Then, this assumption is tested on each example by comparing the number of evaluations required to estimate $I_1$ vs $I_2$. This is a reasonable assumption since $I_1$ contains a factor $f(\vx)f(\vx')$ (not appearing in $I_2$) which could increase the effective dimension of its homologous $f(\vx)$. While it is true that in QMC the nominal dimension might not be very telling, this happens in particular cases such as RKHS with dimension weights satisfying some specific properties. Since for Sobol' indices we consider integrands resulting from products of the same function with different independent inputs, considering the original RKHS might not be enough and the resulting effective dimension might increase.}
%plotting the repartition of the sum of the $c_j$ (equation (19)) over the $100$ repeats. The sign of the sum tells us if, in average, this assumption is validated across the Sobol' indices.}
